Social Visual Analytics: DevOps for Data Scientists

### 2015-03-11 conclusion.tex
yes

We presented a case for an environment that supports the visual
analytics process, from data acquisition and exploratory
data analysis, through development and deployment. One might
think of this approach as ``DevOps for data science.''
The environment supports collaboration and communication
with capabilities for creating and sharing experimental workbooks,
version control, searching, recommending, annotating, and publishing
experiments as web sites and as reusable services.

We implemented these ideas in the RCloud prototype.

Experience with the prototype provides evidence that data
science teams, and the organizations in which they work,
benefit from having such capabilities.

Some possible next steps are to support cross-language development,
to incorporate richer source code analysis and recommendation
techniques, to provide fine-grained security, and to improve
the usability of the HTML5 human interface.

>>>>

We presented a case for an environment that supports the visual
analytics process, from data acquisition and exploratory
data analysis, through development and deployment.
This approach can be considered ``DevOps for data science''
or reproducible data science.
The environment supports collaboration and communication
with capabilities for creating and sharing experimental workbooks,
version control, searching, recommending, annotating, and publishing
experiments as web sites and as reusable services.

We implemented these ideas in the RCloud prototype.
Experience with the prototype provides evidence that data
science teams and the organizations in which they work
benefit from having such capabilities.

Some possible next steps are to support cross-language development,
to incorporate richer recommendation techniques, to provide fine-grained
information security, and to improve the usability of the human interface.
